### 2018-11-08 submission/manuscript.Rmd
Early edits

@@

@@

>>>>

# Influence of DNA Polymerase on PCR bias, chimera formation, and errors when sequencing 16S rRNA genes from complex communities

@@

16S rRNA gene sequencing is a widely used tool for surveying the structure of microbial communities
* Numerous sources of bias ranging from sample preservation, extraction, primers, PCR, and sequencing
* PCR and sequencing errors can also influence our ability to accurately describe the structure of the communities
* Within a study, it is unlikely that samples would be differentially affected by these sources of bias; however, if we want to compare the results of one study to another, the results are likely to be confounded by the differences in these biases and sources of error
* There has been great interest in developing bioinformatics tools to account for errors and limited interest in accounting for bias
* There has also been considerable interest in considering how laboratory methods influence biases and errors.
* One area that has not received extensive attention has been the influence of the polymerase on bias and error.

Factors known to influence PCR bias
* Fragment length
* GC content
* Flanking DNA sequence
* Polymerase?
* Complex communities?
* Number of cycles

Factors known to influence chimera rate
* Fragmentation of DNA
* DNA concentration
* Similarity of potential parents
* PCR extension time
* Number of cycles

Factors known to influence polymerase error rates
* Number of cycles
* Proof-reading
* Enzymology

Early work focused on simple mixtures of genomic DNA and 16S rRNA gene fragments to explore PCR biases and chimera formation.
* Have a poor understanding of how polymerase impacts these problems
* Have a poor understanding of how these problems manifest in more complex communities

@@

Quantifying the problems...

* Polymerases' effects on bias
	* Different polymerases and cycle numbers
	* Mock community w/ perfect chimera removal
	* Relative abundance
	* Variation in Shannon/Inverse Simpson diversity across cycle numbers
	* Variation in Bray-Curtis across cycle numbers
	* Impact of fragment length on bias (are they all the same length)
	* Impact of fragment GC content on bias

* Polymerases' effects on error rates
	* Different polymerases and cycle numbers
	* Mock community w/ perfect chimera removal

* Polymerases' effects on chimera rate
	* Different polymerases and cycle numbers
	* Mock community w/ perfect chimera removal

Characterizing the effects...

* Polymerases' effects on bias
	* Different polymerases and cycle numbers
	* Human communities w/ uchime chimera removal
	* Variation in Shannon/Inverse Simpson diversity across cycle numbers
	* Variation in Bray-Curtis across cycle numbers
	* Which factor has biggest influence on beta-diversity - polymerase, cycle number, sample
	* Impact of fragment length on bias (are they all the same length)
	* Impact of fragment GC content on bias

* Detection of chimeras
	* Different polymerases and cycle numbers
	* Use Mock community data
	* Use uchime to remove chimeras to get residual chimera rate
	* Error rate vs residual chimera rate
